Enrich the datasets with new columns.

### 2020-08-27 inst/analysis/analysis_stable.Rmd
Figures with legend
Environments table

@@

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
theme_update(text = element_text(size = 20))

@@

```{r envirall}
classified_envir %>% ggplot() +
  geom_bar(aes(x =fct_rev(fct_infreq(env_class)), weight = nb_ev_calls )) +
  coord_flip() +
  scale_y_log10() +
  labs(x = "Environments") + 
  facet_wrap(~dataset)

@@

```{r envir_read}
classified_envir %>% ggplot() +
  geom_bar(aes(x =fct_rev(fct_infreq(env_class_read)), weight = nb_ev_calls )) +
  coord_flip() +
  scale_y_log10() +
  labs(x = "Environments") + 
  facet_wrap(~dataset)

@@

>>>>

save_table <- function(df, fname) {
  df %>%
    xtable::xtable(align="lXrrrr") %>%
    print(
      tabular.environment = "tabularx", 
      width = "\\textwidth",
      floating=F,
      file=fname,
      include.rownames=F
    )
}

@@

source("inc/paths.R")
source("inc/latextags.R")
source("inc/setup.R")
theme_set(theme_minimal())
#theme_update(text = element_text(size = 16))

@@

```{r envirall}
classified_envir %>% 
  ggplot() +
  geom_bar(aes(x =fct_rev(fct_infreq(env_class)), weight = nb_ev_calls )) +
  coord_flip() +
  labs(x = "Environments") + 
  facet_wrap(~dataset)

@@

```{r envir_read}
classified_envir %>% ggplot() +
  geom_bar(aes(x =fct_rev(fct_infreq(env_class_read)), weight = nb_ev_calls )) +
  coord_flip() +
  labs(x = "Environments") + 
  facet_wrap(~dataset)

@@

```{r}
classified_envir_prop_core <- classified_envir %>% 
  filter(dataset == "core") %>%
  count(env_class, wt = nb_ev_calls, sort = TRUE) %>%
  mutate(proportion = n / sum(n))

classified_envir_prop_packages <- classified_envir %>% 
  filter(dataset == "packages") %>%
  count(env_class, wt = nb_ev_calls, sort = TRUE) %>%
  mutate(proportion = n / sum(n))

classified_envir_prop_core %>%
  head(5) %>%
  add_column(index = toupper(letters)[1:5]) %>%
  pmap_dfr(function(env_class, n, proportion, index)
  {
    r(paste("core", "env class", index), env_class)
    r(paste("core", "count", index), n)
    r(paste("core", "proportion", index), percent(proportion))
  })

classified_envir_prop_packages %>%
  head(5) %>%
  add_column(index = toupper(letters)[1:5]) %>%
  pmap_dfr(function(env_class, n, proportion, index)
  {
    r(paste("packages", "env class", index), env_class)
    r(paste("packages", "count", index), n)
    r(paste("packages", "proportion", index), percent(proportion))
  })
```

### 2020-08-27 inst/analysis/enrich_dataset.Rmd
Environments table

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE)

>>>>

```{r setup, include=FALSE}
knitr::knit_hooks$set(time_it = local({
  now <- NULL
  function(before, options) {
    if (before) {
      # record the current time before each chunk
      now <<- Sys.time()
    } else {
      # calculate the time difference after a chunk
      res <- difftime(Sys.time(), now)
      # return a character string to show the time
      paste("Time for this code chunk to run:", res, unit(res))
    }
  }
}))

knitr::opts_chunk$set(echo = TRUE,
                      fig.retina = 2,
                      fig.width = 10,
                      cache.lazy = FALSE,
                      time_it = TRUE)
